Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2020-05-18 bbbq_article.tex
EOD
Fix makefile and references

Also for MHC-II, there are multiple computational tools developed 
to predict epitopes,
such as using a trained neural network (\cite{nielsen2003reliable})
or a Gibbs sampling approach (\cite{nielsen2004improved}).
According to \cite{lundegaard2011prediction}, in 2011,
from a set of multiple tools, 
NetMHCIIpan (\cite{nielsen2008quantitative,karosiene2013netmhciipan})
gave rise to the most accurate predictions.
Later tools are \cite{zhang2013predicting},
\cite{trolle2014nettepi} and \cite{zhang2015accurate}.
In this study, we'll be using \richel{Pick FOSS tool here}

@@

For MHC-I, it was found that predicted epitopes derived 
from human transmembrane helices (TMHs)
are over-presented by all 5 HLA-A and 
most of 8 HLA-B super types (\cite{bianchi2017}).
One explanation is that the presentation of TMHs 
may have an evolutionary advantage for 
the (human) host, as TMHs have a reduced variability 
due to the functional requirement of being able to span a lipid bilayer. 
Due to this, pathogens have a lower chance to develop an escape mutation,
as many mutations will result in a disfunctional TMH.
Note that the mechanism by which a cell presents its TMHs is
yet unknown.

@@

The effective number of epitopes, however,
is much lower than the actual number of possible
epitopes, due to immunodominance. 
Immunodominance is a feature of the immune system,
due to which some epitopes dominate in causing an immune response,
where other (called subdominant) epitopes end up having no 
effect \cite{akram2012immunodominance}.
The same study mentions 20 factors that influence the strength
of an immune response.
The most relevant factor for this study is the effect of
a mutation within an epitope, 
such as the in vitro example described in \cite{berkhoff2004mutation},
where one single mutation resulted in a 5-20\% weaker
responese of virus-specific CD8+ T cells \richel{Fun experiment:
do this in silico}.
Due to immunodominance, we dare assume that there can be selection
for immune system avoidance, as the effective number of loci may be
low and effects of a single mutation noticable.

>>>>

Also for MHC-II, there are multiple computational tools developed 
to predict epitopes,
such as using a trained neural network (\cite{nielsen2003reliable})
or a Gibbs sampling approach (\cite{nielsen2004improved}).
According to \cite{lundegaard2011prediction}, in 2011,
from a set of multiple tools, 
NetMHCIIpan (\cite{nielsen2008quantitative,karosiene2013netmhciipan})
gave rise to the most accurate predictions.
Later tools are \cite{zhang2013predicting},
\cite{trolle2014nettepi}, \cite{zhang2015accurate}
and the very recent MHCnuggets\cite{shao2020high}.
In this study, we'll be using MHCnuggets, as it is the only FOSS tool available.

@@

For MHC-I, it was found that predicted epitopes derived 
from human transmembrane helices (TMHs)
are over-presented by all 5 HLA-A and 
most of 8 HLA-B super types (\cite{bianchi2017}).
One explanation is that the presentation of TMHs 
may have an evolutionary advantage for 
the (human) host, as TMHs have a reduced variability 
due to the functional requirement of being able to span a lipid bilayer. 
Due to this, pathogens have a lower chance to develop an escape mutation,
as many mutations will result in a dysfunctional TMH.
Note that the mechanism by which a cell presents its TMHs is
yet unknown.

@@

The effective number of epitopes, however,
is much lower than the actual number of possible
epitopes, due to immunodominance. 
Immunodominance is a feature of the immune system,
due to which some epitopes dominate in causing an immune response,
where other (called subdominant) epitopes end up having no 
effect \cite{akram2012immunodominance}.
The same study mentions 20 factors that influence the strength
of an immune response.
The most relevant factor for this study is the effect of
a mutation within an epitope, 
such as the in vitro example described in \cite{berkhoff2004mutation},
where one single mutation resulted in a 5-20\% weaker
response of virus-specific CD8+ T cells \richel{Fun experiment:
do this in silico}.
Due to immunodominance, we dare assume that there can be selection
for immune system avoidance, as the effective number of loci may be
low and effects of a single mutation noticeable.
